### 2022-05-27 main/chapter_2ljets.tex
S to \Omega, include metsig ratio form

Signal $b$-tagged jets require $\pt > 20\,\eV[G]$, $|\eta| < 2.5$ and a tag from
the `MV2c10' algorithm at its $77\%$ efficiency working point.
\TODO{cite, summarize}

@@

Uncertainty in $\ptmiss$ is modelled for $\metsig$ by a covariance matrix, $S$,
in the transverse plane, and used to define
\begin{equation}
\metsig
=
\ptmiss S^{-1} \ptmiss
,
\end{equation}
which can be rearranged into a ratio of $(\met)^2$ to a function of elements
of the covariance matrix~\cite{atlas_met_significance}.
This is the square of a Mahalanobis (standard-deviations) distance between
the origin and $\ptmiss$~\cite{mahalanobis1936generalised}.

Just as $\ptmiss$ is constructed from a (negative) sum of contributions from
objects in an event,
$S$ is a sum of covariances assigned to those objects;
both means and variances add linearly.

>>>>

Signal $b$-tagged jets require $\pt > 20\,\eV[G]$, $|\eta| < 2.5$ and a tag from
the `MV2c10' algorithm at its $77\%$ efficiency working point.
This tagging algorithm uses
\cite{atlas_jet_mv2c10_2017, atlas_jet_tagging_2019}
\TODO{cite, summarize}
%
boosted decision tree~\cite{friedman2002stochastic}

@@

Uncertainty in $\ptmiss$ is modelled for $\metsig$ by a covariance matrix
$\Omega$ in the transverse plane, and used to define
\begin{equation}
\metsig
=
\ptmiss \Omega^{-1} \ptmiss
=
\frac{(\met)^2}{\sigma_L^2(1 - \rho_{LT}^2)}
,
\end{equation}
in which $\sigma_L^2$ is the variance in the direction of $\ptmiss$ and
$\rho_{LT}$ is the correlation coefficient between the parallel and
perpendicular components~\cite{atlas_met_significance}.
This is the square of a Mahalanobis (standard-deviations) distance between
the origin and $\ptmiss$~\cite{mahalanobis1936generalised}.

Just as $\ptmiss$ is constructed from a (negative) sum of contributions from
objects in an event,
$\Omega$ is a sum of covariances assigned to those objects;
both means and variances add linearly.
